Challenges in Developing Great Quasi-Monte Carlo Software

### 2023-03-06 MCQMC2022ChallengesQMCSoftwareArticle.tex
Updates from Overleaf

SciPy and PyTorch's original implementations of Sobol' sequences omitted the first point.  The rationale was that the unscrambled first point of the Sobol' sequence is $\bsx_1 = \bszero$, which becomes the undesirable $\boldsymbol{-\infty}$ when transformed to mimic a Gaussian distribution.  A vigorous discussion ensued \cite{scipySobol2020a}, which prompted an article by Art Owen \cite{Owe22a} on why one should not drop the first point and destroy the digital net structure.  Instead one should randomly scramble the Sobol' sequence (and other LD sequences) so that $\bsx_1 \ne \bszero$.  Although SciPy and PyTorch were corrected, other software libraries with LD sequence generators still omit the first point.

>>>>

SciPy and PyTorch's original implementations of Sobol' sequences omitted the first point.  The rationale was that the unscrambled first point of the Sobol' sequence is $\bsx_1 = \bszero$, which becomes the undesirable $\boldsymbol{-\infty}$ when transformed to mimic a Gaussian distribution.  A vigorous discussion ensued \cite{scipySobol2020a,pytorchSoboldiscussion2020a}, which prompted an article by Art Owen \cite{Owe22a} on why one should not drop the first point and destroy the digital net structure.  Instead one should randomly scramble the Sobol' sequence (and other LD sequences) so that $\bsx_1 \ne \bszero$.  Although SciPy and PyTorch were corrected, other software libraries with LD sequence generators still omit the first point.
